On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-03-27 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Edits from Usachev

\paragraph{Abstract.}
	A planar integral point set is a set of non-collinear points in plane
	such that for any pair of the  points the Euclidean distance
	between the points is integral.
	We discuss the classification of planar integral point sets
	and provide examples of sets that are not covered by the existent classification.

@@

How do we describe an integral point set?
For example, with the number of points in it, which is always finite~\cite{anning1945integral,erdos1945integral}
and is said to be the \emph{cardinality} of the IPS.
Furthermore, we can naturally % TODO: naturally/essentially? cf. arxiv/1
define the diameter of a finite point set.

@@

It's notable that any of the examples that are discussed below
is located on a union of at most three straight lines.
%In the most pictures these lines are shown as solid lines.
For classification of planar IPS that are located on a union of two straight lines,
we refer the reader to~\cite{avdeev2019particular}.

@@

\begin{dfn}
	A planar integral point sets of $n$ points with $n-1$ points on a straight line is called
	a \textit{facher} set.
\end{dfn}
Facher sets are very dominating examples of planar integral point sets.
In~\cite{antonov2008maximal}, facher sets of characteristic 1 are called \textit{semi-crabs}.
%For $9 \leq n \leq 122$, the diameter $d(2,n)$ is reached on a facher point set~\cite{kurz2008minimum}.

@@

Figure~\ref{8_with_many_common} shows an example of three PIPS of cardinality 8,
each pair of that shares 6 or 7 points but cannot be united into another PIPS.

@@

On Figures~\ref{10_2431_1_0606} and~\ref{15_19203744_1_80db}, another examples of arrow-like IPSs are shown.
The one on Figure~\ref{15_19203744_1_80db} is obtained from the one on Figure~\ref{10_2431_1_0606}
by dilation and looking for points on $x$ axis.

@@

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by reflecting relatively to the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.
%
%TODO: write about points which prevent the set from reflection
%
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{multline}
%
\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

>>>>

\paragraph{Abstract.}
	A planar integral point set is a set of non-collinear points in plane
	such that for any pair of the  points the Euclidean distance
	between them is integral.
	We discuss the classification of planar integral point sets
	and provide examples of sets that are not covered by the existent classification.

@@

How do we describe an integral point set?
For example, by the number of points in it, which is always finite~\cite{anning1945integral,erdos1945integral}
and is said to be the \emph{cardinality} of the IPS.
Furthermore, we can naturally % TODO: naturally/essentially? cf. arxiv/1
define the diameter of a finite point set.

@@

Note that all examples that are discussed below are
located on a union of at most three straight lines.
%In the most pictures these lines are shown as solid lines.
For classification of planar IPS that are located on a union of two straight lines,
we refer the reader to~\cite{avdeev2019particular}.

@@

\begin{dfn}
	A planar integral point sets of $n$ points with $n-1$ points on a straight line is called
	a \textit{facher} set.
\end{dfn}
Facher sets are predominant examples of planar integral point sets.
In~\cite{antonov2008maximal}, facher sets of characteristic 1 are called \textit{semi-crabs}.
%For $9 \leq n \leq 122$, the diameter $d(2,n)$ is reached on a facher point set~\cite{kurz2008minimum}.

@@

Figure~\ref{8_with_many_common} shows an example of three PIPS of cardinality 8,
each pair of that shares 6 or 7 points but cannot be combined into another PIPS.

@@

On Figures~\ref{10_2431_1_0606} and~\ref{15_19203744_1_80db}, other examples of arrow-like IPSs are shown.
The one on Figure~\ref{15_19203744_1_80db} is obtained from the one on Figure~\ref{10_2431_1_0606}
by dilation and looking for points on $x$ axis.

@@

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by the reflection in the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.
%
%TODO: write about points which prevent the set from reflection
%
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{multline}
%
\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}
